---
title: "R Notebook"
output: html_notebook
---

Album/Artist Analysis

Load Libraries
```{r}
library(spotifyr)
library(plyr)
library(tidyverse)
library(ggthemes)
library(ggridges)
library(knitr)
library(kableExtra)
library(lubridate)
library(jsonlite)
library(gghighlight)
library(ggplot2)
library(plotly)
```

Authorisation
```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = "052dec7a99bd42e888548b0f32f5d444")
Sys.setenv(SPOTIFY_CLIENT_SECRET = "3e61d71877f2486fa2a17c703eb452a6")
access_token <- get_spotify_access_token(client_id = Sys.getenv('SPOTIFY_CLIENT_ID'), client_secret = Sys.getenv('SPOTIFY_CLIENT_SECRET'))
```
taylor3 <- read_csv("~/Desktop/Github/spotify/plots/taylor.csv")

DF of an Artist
```{r}
MM <- get_artist_audio_features('Modest Mouse')
taylor <- get_artist_audio_features('Taylor Swift')
```


```{r}
#Create string you want to filter
taylor_albums1 <- c("Taylor Swift", "Fearless", "Speak Now", "Red", "1989", "reputation", "Lover", "Folklore", "evermore")

#subset of the albums you want
taylor1 <- taylor %>%
dplyr::filter(album_name %in% taylor_albums1)

#checking if it worked
taylor1 %>%
  dplyr::distinct(album_name)

#Create as factor
taylor1$album_name <- as.factor(taylor1$album_name)
taylor1$album_release_year <- as.factor(taylor1$album_release_year)

#order the factor
taylor1$album_name <- factor(taylor1$album_name, levels = unique(taylor1$album_name[order(taylor1$album_release_year)])) 
taylor1$album_release_year <- factor(taylor1$album_release_year, levels = unique(taylor1$album_release_year[order(taylor1$album_release_year)]))

#rename factors, might need to reorder the factors after this
taylor1$album_name <- recode_factor(taylor1$album_name, evermore = "Evermore", reputation = "Reputation")
```


Create Factors for categorical data
```{r}
MM$album_name <- as.factor(MM$album_name)
MM$album_release_year <- as.factor(MM$album_release_year)

```

Energy By Album
```{r}
t_plot1 <- taylor1 %>%
  ggplot(aes(x = energy, y = fct_rev(album_name))) +
               geom_density_ridges(scale = 2, size = 0.1, rel_min_height = 0.03,quantile_lines=TRUE,quantiles=2) +
               theme_ridges() +
               scale_x_continuous(expand = c(0, 0)) +
               labs(title= "Taylor Swift energy by album", subtitle = "Based on data from Spotify", y="Album", x = "Energy")
             

t_plot2 <- taylor1 %>%
  ggplot(aes(x = energy, y = fct_rev(album_name), fill = album_name)) +
               geom_density_ridges(scale = 2, size = 0.1, rel_min_height = 0.03,quantile_lines=TRUE,quantiles=2) +
               theme_ridges() +
               scale_x_continuous(expand = c(0, 0)) +
               labs(title= "Taylor Swift energy by album", subtitle = "Based on data from Spotify", y="Album", x = "Energy")
```

Energy plots
```{r}
t_plot2 + theme_wsj() + scale_fill_brewer(palette = "Pastel1")
ggsave("pastel1_wsj_energy_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot2 + theme_solarized() + scale_fill_brewer(palette = "Pastel1")
ggsave("pastel1_solarized_energy_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot2 + scale_color_fivethirtyeight() + theme_fivethirtyeight()
ggsave("fivethirtyeight_energy_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot2 + theme_solarized() + scale_colour_solarized()
ggsave("solarized_energy_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")
```


Energy By Album
```{r}
ggplot(MM, aes(x = energy,y=fct_rev(album_release_year))) + 
  geom_density_ridges(scale = 2, size = 0.1, rel_min_height = 0.03,quantile_lines=TRUE,quantiles=2) +
  theme_ridges()+
  scale_y_discrete(labels=levels(MM$album_name)) + 
  scale_x_continuous( expand = c(0, 0)) +
  labs(title= "Modest Mouse energy by album",subtitle = "Based on data from Spotify", y="Album", x = "Energy")
```


Valence plots
```{r}
t_plot3 <- taylor3 %>%
  ggplot(aes(x = valence, y = fct_rev(album_name), fill = album_name)) +
               geom_density_ridges(scale = 2, size = 0.1, rel_min_height = 0.03,quantile_lines=TRUE,quantiles=2) +
               theme_ridges() +
               scale_x_continuous(expand = c(0, 0)) +
               labs(title= "Taylor Swift valence by album", subtitle = "Based on data from Spotify", y="Album", x = "Valence")


t_plot3 + theme_wsj() + scale_fill_brewer(palette = "Pastel1")
ggsave("pastel1_wsj_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot3 + theme_solarized() + scale_fill_brewer(palette = "Pastel1")
ggsave("pastel1_solarized_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot3 + scale_color_fivethirtyeight() + theme_fivethirtyeight()
ggsave("fivethirtyeight_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot3 + theme_solarized() + scale_colour_solarized()
ggsave("solarized_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")
```

Dance plots
```{r}
t_plot4 <- taylor3 %>%
  ggplot(aes(x = danceability, y = fct_rev(album_name), fill = album_name)) +
               geom_density_ridges(scale = 2, size = 0.1, rel_min_height = 0.03,quantile_lines=TRUE,quantiles=2) +
               theme_ridges() +
               scale_x_continuous(expand = c(0, 0)) +
               labs(title= "Taylor Swift danceability by album", subtitle = "Based on data from Spotify", y="Album", x = "Danceability")

t_plot4 + theme_wsj() + scale_fill_brewer(palette = "Pastel1")
ggsave("pastel1_wsj_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot4 + theme_solarized() + scale_fill_brewer(palette = "Pastel1")
ggsave("pastel1_solarized_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot4 + scale_color_fivethirtyeight() + theme_fivethirtyeight()
ggsave("fivethirtyeight_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")

t_plot4 + theme_solarized() + scale_colour_solarized()
ggsave("solarized_valence_by_album.png", path = "~/Desktop/Github/spotify/plots/taylor_swift")
```
Corr
```{r}
taylor3 %>%
  dplyr::select(tempo, energy, valence, danceability, duration_ms, loudness, instrumentalness, -track_name, -album_name) %>%
  scale() %>%
  cor() %>%
  corrplot::corrplot(method = 'color', 
                     order = 'hclust', 
                     type = 'upper', 
                     diag = FALSE, 
                     tl.col = 'black',
                     addCoef.col = "grey30",
                     number.cex = 0.6,
                     col = colorRampPalette(colors = c(
                       kp_cols('red'), 
                       'white', 
                       kp_cols('dark_blue')))(200),
                     main = 'Audio Feature Correlation',
                     mar = c(2,4,5,4),
                     family = 'Avenir')
```
"danceability", "energy", "key", "loudness", "instrumentalness", "valence", "tempo", "duration_ms"

danceability, energy, key, loudness, instrumentalness, valence, tempo, duration_ms


A table representation of the same data:
```{r}
MM %>% 
  group_by(album_name) %>% 
  summarise(avg = mean(energy),max = max(energy),min = min(energy)) %>% 
  arrange(-avg) %>% kable() %>% 
  kable_styling("striped", full_width = F, position = "left")%>% 
  row_spec(row = 1, color = "black",bold = TRUE)
```

A table representation of the same data: Taylor
```{r}
taylor1 %>% 
  group_by(album_name) %>% 
  summarise(avg = mean(energy),max = max(energy),min = min(energy)) %>% 
  arrange(-avg) %>% 
  kable(caption = "Taylor Swift energy by album") %>% 
  kable_styling("striped", full_width = F, position = "left")%>% 
  row_spec(row = 1, color = "black",bold = TRUE) 

taylor1 %>% 
  group_by(album_name) %>% 
  summarise(avg = mean(valence),max = max(valence),min = min(valence)) %>% 
  arrange(-avg) %>% 
  kable(caption = "Taylor Swift valence by album") %>% 
  kable_styling("striped", full_width = F, position = "left")%>% 
  row_spec(row = 1, color = "black",bold = TRUE) 

taylor1 %>% 
  group_by(album_name) %>% 
  summarise(avg = mean(danceability),max = max(danceability),min = min(danceability)) %>% 
  arrange(-avg) %>% 
  kable(caption = "Taylor Swift danceability by album") %>% 
  kable_styling("striped", full_width = F, position = "left")%>% 
  row_spec(row = 1, color = "black",bold = TRUE) 
```
Energy table
```{r}
table1 <- taylor3 %>% 
  group_by(album_name) %>% 
  summarise(avg = mean(energy),max = max(energy),min = min(energy)) %>% 
  arrange(-avg) %>% 
  kable(caption = "Taylor Swift energy by album") %>% 
  kable_styling("striped", full_width = F, position = "left")%>% 
  row_spec(row = 1, color = "black",bold = TRUE) 

reactable(taylor3, bordered = TRUE, highlight = TRUE)

reactable(taylor3, groupBy = "album_name", columns = list(
  energy = colDef(aggregate = "max"),
  energy = colDef(aggregate = "min"),
  energy = colDef(aggregate = "mean", format = colFormat(digits = 1))))
          
          
reactable(taylor3, groupBy = "album_name", columns = list(
  energy = colDef(aggregate = "mean", format = colFormat(digits = 2))))

reactable(taylor3, columns = list(
  energy = colDef(name = "Energy"),
  valence = colDef(name = "Valence"),
  danceability = colDef(name =  "Danceability")
))


  reactable(taylor3, groupBy = "album_name",
  defaultColDef = colDef(
    header = function(value) gsub(".", " ", value, fixed = TRUE),
    cell = function(value) format(value, nsmall = 1),
    align = "center",
    minWidth = 70,
    headerStyle = list(background = "#f7f7f8")),
  columns = list(
    track_name = colDef(minWidth = 140),
    album_name = colDef(minWidth = 140)),
  bordered = TRUE, highlight = TRUE)
  
  
reactable(taylor3, groupBy = "album_name", columns = list(
  energy = colDef(aggregate = "mean", format = colFormat(digits = 2)),
  valence = colDef(aggregate = "mean", format = colFormat(digits = 2)),
  danceability = colDef(aggregate = "mean", format = colFormat(digits = 2))
))  

orange_pal <- function(x) rgb(colorRamp(c("#ffe4cc", "#ffb54d"))(x), maxColorValue = 255)
blue_pal <- function(x) rgb(colorRamp(c("#ccdeff", "#4dafff"))(x), maxColorValue = 255)
pink_pal <- function(x) rgb(colorRamp(c("#eda8e1", "#f26bdb"))(x), maxColorValue = 255)
GnYlRd <- function(x) rgb(colorRamp(c("#63be7b", "#ffeb84", "#f87274"))(x), maxColorValue = 255)

taylor3 <- taylor3 %>%
  relocate(album_release_year, .after = duration_ms) %>%
  relocate(valence, .before = danceability)
  
taylor3 <- taylor3 %>%
  dplyr::select(-key, -loudness, -instrumentalness)


reactable(
  taylor3, resizable = TRUE,
  filterable = TRUE,
  searchable = TRUE,
  highlight = TRUE,
  columns = list(
    danceability = colDef(
      style = function(value) {
        normalized <- (value - min(taylor3$danceability)) / (max(taylor3$danceability) - min(taylor3$danceability))
        color <- GnYlRd(normalized)
        list(background = color)
      }),
    valence = colDef(
      style = function(value) {
        normalized <- (value - min(taylor3$valence)) / (max(taylor3$valence) - min(taylor3$valence))
        color <- GnYlRd(normalized)
        list(background = color)
      }),
    energy = colDef(
      style = function(value) {
        normalized <- (value - min(taylor3$energy)) / (max(taylor3$energy) - min(taylor3$energy))
        color <- GnYlRd(normalized)
        list(background = color)
      }
    ),
    album_release_year = colDef(minWidth = 160)
  )
)



```

```{r}
reactable(
  taylor3,
  columns = list(
    valence = colDef(
    
    
    energy = colDef(
      style = function(value) {
        normalized <- (value - min(taylor3$energy)) / (max(taylor3$energy) - min(taylor3$energy))
        color <- orange_pal(normalized)
        list(background = color)
      }
    )
  )
)
```

reactable(
  temps,
  defaultColDef = colDef(
    style = function(value) {
      if (!is.numeric(value)) return()
      normalized <- (value - min(nottem)) / (max(nottem) - min(nottem))
      color <- GnYlRd(normalized)
      list(background = color)
    },
    format = colFormat(digits = 1),
    minWidth = 50
  ),
  columns = list(
    .rownames = colDef(name = "Year", sortable = TRUE, align = "left")
  ),
  bordered = TRUE
)

```{r}
reactable(data, columns = list(
  
  
  Petal.Length = colDef(style = function(value) {
    normalized <- (value - min(data$Petal.Length)) / (max(data$Petal.Length) - min(data$Petal.Length))
    color <- orange_pal(normalized)
    list(background = color)
  })
,
data$Species = colDef(name = "Species"))
)
```

```{r}
reactable(taylor3, columns = list(
  Change = colDef(
    cell = function(value) {
      if (value >= 0) paste0("+", value) else value
    },
    style = function(value) {
      color <- if (value > 0) {
        "#008000"
      } else if (value < 0) {
        "#e00000"
      }
      list(fontWeight = 600, color = color)
    }
  )
))
```



reactable(taylor_df, groupBy = "Album")

Analysis of a specific album
```{r}
MM %>%
  arrange(track_number) %>% 
  filter(album_name == 'Strangers to Ourselves') %>%
  select(track_name,track_number,energy,valence,tempo) %>% 
  mutate(
    energy = cell_spec(energy, "html", bold = ifelse(energy == max(energy), TRUE, FALSE)),
    valence = cell_spec(valence, "html", bold = ifelse(valence == max(valence), TRUE, FALSE))
  ) %>%
  kable(format = 'html',escape=F) %>% 
  kable_styling("striped", full_width = F, position = "left",bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


```{r}
taylor3 <- taylor1 %>%
  dplyr::group_by(album_name) %>%
  dplyr::distinct(track_name, .keep_all = TRUE)
  
#Patterns to be removed from the data
remove.list <- paste(c("Demo Recording", "Karaoke Version", "Pop Version", "Acoustic Version"), collapse = '|')

#Applying the changes
taylor3 <- taylor3 %>%
  filter(!grepl(remove.list, track_name)) 

taylor3 <- taylor3 %>%
  dplyr::select(artist_name, track_name, album_name, album_release_year, danceability, energy, key, loudness, instrumentalness, valence, tempo, duration_ms)
```


