---
title: "offline_stream_history_graphs"
author: "Justyn"
date: "2/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Redo these graphs with the new data, save them with HQ
Compare your df with changing it from long to wide

```{r}
library(jsonlite)
library(lubridate)
library(gghighlight)
library(spotifyr)
library(tidyverse)
library(knitr)
library(ggplot2)
library(plotly)
```



Playback Activity Per Week and Hours
```{r cache = TRUE}
mySpotify_hours <- streamHistory %>% 
  as_tibble() %>% 
  mutate_at("endTime", ymd_hm) %>% 
  mutate(endTime = endTime - hours(6)) %>% 
  mutate(date = floor_date(endTime, "day") %>% as_date, seconds = msPlayed / 1000, minutes = seconds / 60)

streamingHours <- mySpotify_hours %>% 
  filter(date >= "2020-01-01") %>% 
  group_by(date) %>% 
  group_by(date = floor_date(date, "week")) %>%
  summarize(hours = sum(minutes) / 60) %>% 
  arrange(date) %>% 
  ggplot(aes(x = date, y = hours)) + 
  geom_col(aes(fill = hours)) +
  scale_fill_gradient(low = "yellow", high = "red") + 
  labs(x= "Date", y= "Hours of music playback") + 
  ggtitle("On what dates I've listened to more or less music on Spotify?", "Playback activity per week")

ggsave("playback_activity_week.png", path = "~/Desktop/Github/spotify/plots")
```


Playback Activity Per Specific Artist #Not a huge fan of this. 
```{r cache = TRUE}
hoursArtist <- mySpotify_hours %>% 
  group_by(artistName, date = floor_date(date, "month")) %>% 
  summarize(hours = sum(minutes) / 60) %>% 
  ggplot(aes(x = date, y = hours, group = artistName, colour = artistName)) + 
  labs(x= "Date", y= "Hours of music playback") + 
  ggtitle("On what dates I've listened to more or less music by a specific artist?", "E.g: The Gaslight Anthem and Modest Mouse") +
  geom_line() + 
  gghighlight(artistName == "The Gaslight Anthem" || artistName == "Brian Fallon")

hoursArtist
```


Most Listened Artist (More Than 3 Hours)

```{r cache = TRUE}
minutesMostListened <- mySpotify_hours %>% 
  filter(date >= "2020-01-01") %>% 
  group_by(artistName) %>% 
  summarize(minutesListened = sum(minutes)) %>% 
  filter(minutesListened >= 180) %>%
  ggplot(aes(
    x = reorder(artistName, -minutesListened), 
    y = minutesListened)) + 
  geom_col(aes(fill = minutesListened)) +
  scale_fill_gradient(low = "yellow", high = "red") + 
  labs(x= "Artist", y= "Minutes of music playback") + 
  ggtitle("What were the most listened artists on my Spotify?", "> 3 hours listened") +
  theme(axis.text.x = element_text(angle = 90))

ggsave("artist_more_3_hours.png", path = "~/Desktop/Github/spotify/plots")

minutesMostListened
```
```{r cache=TRUE}

minutesMostListened1 <- mySpotify_hours %>% 
  filter(date >= "2020-01-01") %>% 
  group_by(artistName) %>% 
  summarise(playcount = n()) %>% 
  filter(playcount >= 70) %>%
  ggplot(aes(
    x = reorder(artistName, -playcount), 
    y = playcount)) + 
  geom_col(aes(fill = playcount)) +
  scale_fill_gradient(low = "yellow", high = "red") + 
  labs(x= "Artist", y= "Minutes of music playback") + 
  ggtitle("What were the most listened artists on my Spotify?", "> 70 plays") +
  theme(axis.text.x = element_text(angle = 90))

ggsave("artist_more_70_plays.png", path = "~/Desktop/Github/spotify/plots")
```


Playback Activity By Date and Time of Day
```{r cache = TRUE}
timeDay <- mySpotify %>% 
  filter(date >= "2020-01-01") %>% 
  group_by(date, hour = hour(endTime)) %>% 
  summarize(minutesListened = sum(minutes)) %>% 
  ggplot(aes(x = hour, y = date, fill = minutesListened)) + 
  geom_tile() + 
  labs(x= "Time of the day", y= "Date") + 
  ggtitle("When has there been more playback activity on my Spotify?", "Activity by date and time of day") +
  scale_fill_gradient(low = "yellow", high = "red")

timeDay

ggsave("activity_date_time.png", path = "~/Desktop/Github/spotify/plots")
```


Playback Activity By Time of Day
```{r cache = TRUE}
hoursDay <- mySpotify %>% 
  filter(date >= "2019-01-01") %>% 
  group_by(date, hour = hour(endTime), weekday = wday(date, label = TRUE))%>% 
  summarize(minutesListened = sum(minutes))

hoursDay %>% 
  ggplot(aes(x = hour, y = minutesListened, group = date)) + 
  geom_col(fill = "#ff6600") +
  labs(x= "Time of the day", y= "Minutes of music playback") + 
  ggtitle("What time of day I've listened to the most music on Spotify?", "Activity from 0 to 24 hours")

ggsave("activity_time_of_day_bar.png", path = "~/Desktop/Github/spotify/plots")
```



Playback Activity By Time of Day and Weekday
```{r cache = TRUE}
hoursDay %>% 
  group_by(weekday, hour) %>% 
  summarize(minutes = sum(minutesListened)) %>% 
  ggplot(aes(x = hour, weekday, fill = minutes)) + 
  geom_tile() + 
  scale_fill_gradient(low = "yellow", high = "red") +
  labs(x= "Time of the day", y= "Weekday") + 
  ggtitle("What weekday and time of day I've listened to the most music on Spotify?", "Weekly activity from 0 to 24 hours")

ggsave("activity_day_plus_time_tile.png", path = "~/Desktop/Github/spotify/plots")
```


Playback Activity By Time of Day and Weekday - Linechart
```{r cache = TRUE}
weekDay <- hoursDay %>% 
  group_by(weekday, hour) %>% 
  summarize(minutes = sum(minutesListened)) %>% 
  ggplot(aes(x = hour, y = minutes, color = weekday)) + 
  geom_line() +
  labs(x= "Time of the day", y= "Minutes of music playback") + 
  ggtitle("What weekday and time of day I've listened to the most music on Spotify?", "Line chart - Weekly activity from 0 to 24 hours") 
```


Playback Activity By Day Type
```{r cache = TRUE}
dayType <- hoursDay %>% 
  mutate(day_type = if_else(weekday %in% c("Sat", "Sun"), "weekend", "weekday")) %>% 
  group_by(day_type, hour) %>% 
  summarize(minutes = sum(minutesListened)) %>% 
  ggplot(aes(x = hour, y = minutes, color = day_type)) + 
  geom_line() +
  labs(x= "Time of the day", y= "Minutes of music playback") + 
  ggtitle("What day type I've listened to the most music on Spotify?", "Weekday and weekend activity from 0 to 24 hours") 
```




















