---
title: "R Notebook"
output: html_notebook
---

Project Notes

This will be where you can write/add your notes to help keep yourself more organised

Artist quad is done as well as the corrplot, now you might want to compare correlations of other features between artists?

Offline_stream_history is where you have the data of your spotify stream history. You did some cleaning to make the DF more useful.  


If you want to analyse specifics of the music, use spotifyr
Check the differences for

Short
```{r}
get_my_top_artists_or_tracks(type = tracks, limit = 50,
  time_range = "short_term",
  authorization = get_spotify_authorization_code(),
  include_meta_info = TRUE) #play around with these
```

Medium
```{r}
get_my_top_artists_or_tracks(type = tracks, limit = 50,
  time_range = "medium_term",
  authorization = get_spotify_authorization_code(),
  include_meta_info = TRUE) #play around with these
```  

Long
```{r}
get_my_top_artists_or_tracks(type = tracks, limit = 50,
  time_range = "long_term",
  authorization = get_spotify_authorization_code(),
  include_meta_info = TRUE) #play around with these
```

get_my_recently_played(limit = 50,
  authorization = get_spotify_authorization_code(),
  include_meta_info = TRUE)


get_playlist_audio_features(username, playlist_uris,
  authorization = get_spotify_access_token())



Artist/Albums

Any artists you want to compare against each other
Albums from an artist you want to compare

Compare TGA's albums
Modest Mouse
Ryan Adams

mySpotify

```{r}
mySpotify %>%
  arrange(-playCount)
```
track_num_artist %>%
  mutate(
    freq = case_when(
      n > 100 ~ 'More than 100 tracks',
      between(n, 50, 99) ~ '50~99 tracks',
      between(n, 20, 49) ~ '20~49 tracks',
      TRUE ~ 'Less than 20 tracks'
    )
  ) %>%
  mutate(freq = factor(
    freq,
    levels = c(
      'More than 100 tracks',
      '50~99 tracks',
      '20~49 tracks',
      'Less than 20 tracks'
    )
    ))
  

```{r}
mySpotifyArtist20 <- mySpotifyArtist %>%
  select(artistName, playCount) %>%
  rename(n=playCount) %>%
  top_n(20, n)
```

```{r}
mySpotifyArtist10 <- mySpotifyArtist %>%
  select(artistName, playCount) %>%
  rename(n=playCount) %>%
  top_n(10, n) %>%
  arrange(-n)
```

    
```{r}
mySpotifyArtist10 %>%
  mutate(
    freq = case_when(
      n > 100 ~ 'More than 100 tracks',
      between(n, 50, 99) ~ '50~99 tracks',
      between(n, 20, 49) ~ '20~49 tracks',
      TRUE ~ 'Less than 20 tracks'
    )
  ) %>%
  mutate(freq = factor(
    freq,
    levels = c(
      'More than 100 tracks',
      '50~99 tracks',
      '20~49 tracks',
      'Less than 20 tracks'
    )
  )) %>%
  ggplot(mapping = aes(
    x = reorder(artistName, -n),
    y = n,
    fill = freq
  )) +
  geom_col() +
  labs(fill = NULL,title = 'Who is My Favorite Artist',caption = 'data from spotify via spotify') +
  xlab('Artist') +
  ylab('Tracks Number') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45),
        axis.title = element_text(face = 'bold'),
        plot.title = element_text(hjust = -0.5, face = 'bold', size = 15),
        plot.caption = element_text(hjust = 1,face = 'bold.italic')) 

    
```

```{r}
p.color <- ggplot(data = mySpotifyArtist10, mapping = aes(x = reorder(artistName, -n), y = n, color = n)) 
p.color+geom_col(aes(fill = n) )+ scale_color_gradient()
```

lintr
styler