---
title: "Spotifyr_start"
author: "Justyn"
date: "2/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

He

```{r}
library(jsonlite)
library(lubridate)
library(gghighlight)
library(spotifyr)
library(tidyverse)
library(knitr)
library(ggplot2)
library(plotly)
```

## Including Plots

You can also embed plots, for example:

```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = "052dec7a99bd42e888548b0f32f5d444")
Sys.setenv(SPOTIFY_CLIENT_SECRET = "3e61d71877f2486fa2a17c703eb452a6")
access_token <- get_spotify_access_token(client_id = Sys.getenv('SPOTIFY_CLIENT_ID'), 
                                         client_secret = Sys.getenv('SPOTIFY_CLIENT_SECRET'))
```



```{r}
playlist_username <- 'b7iflt2s6um28zx952r2rp1q9'
```




GET SPECIFIC PLAYLIST FEATURES - on repeat 37i9dQZF1EpljHGqh75Ggn
```{r}
playlist_uris <- c('37i9dQZF1EpljHGqh75Ggn')
playlistOnRepeat <- get_playlist_audio_features(playlist_username, playlist_uris)
```


GET SPECIFIC PLAYLIST FEATURES - repeat rewind 37i9dQZF1EpNiqXss6LbGe
```{r}
playlist_uris <- c('37i9dQZF1EpNiqXss6LbGe')
playlistRepeatRewind <- get_playlist_audio_features(playlist_username, playlist_uris)
```


GET SPECIFIC PLAYLIST FEATURES - top songs 2020 37i9dQZF1EM7wA9HfN3vt4
```{r}
playlist_uris <- c('37i9dQZF1EM7wA9HfN3vt4')
playlistTop2020 <- get_playlist_audio_features(playlist_username, playlist_uris)
```


PLOT LESS POPULARITY TRACKS ON SPECIFIC PLAYLIST
```{r}
playlistOnRepeat %>% 
  group_by(track.popularity) %>% 
  filter(track.popularity <= "35") %>%
  ggplot(aes(x = track.name, y = track.popularity)) + 
  geom_col(aes(fill = track.album.name)) +
  labs(x= "Track name", y= "Popularity") + 
  ggtitle("What are the least popular songs I listen to on Spotify?", "Popularity ranking < 35 in a specific playlist") +
  theme(axis.text.x = element_text(angle = 90))
```



df_new <- df_new %>%
  mutate(popularity_class=case_when(
    track.popularity >= 1 & track.popularity <= 20 ~ "E",
    track.popularity > 20 & track.popularity <= 40 ~ "D",
    track.popularity > 40 & track.popularity <= 60 ~ "C",
    track.popularity > 60 & track.popularity <= 80 ~ "B",
    track.popularity > 80 & track.popularity <= 100 ~ "A"))

###
library(ggjoy)

ggplot(joy, aes(x = valence, y = album_name)) + 
  geom_joy() + 
  theme_joy() +
  ggtitle("Joyplot of Joy Division's joy distributions", 
          subtitle = "Based on valence pulled from Spotify's Web API with spotifyr")

 
library(ggplot2)
library(dplyr)
library(ggpubr)
library(reshape2)


ggplot(df_new, aes(x = acousticness, y = track.popularity, color = popularity_class))+ 
  theme_bw()+ 
  geom_point()+
  scale_color_discrete(name="Category of Popularity", labels=c("A-Popularity > 80","B-Popularity > 60","C-Popularity > 40","D-Popularity > 20","E-Popularity > 1"))+
  labs(x = "Acousticness of track",
       y = "Popularity of track",
       title = "Popularity Vs Acousticness")

df_new$ID <- seq.int(nrow(df_new))

t_c <- sapply(df_new$ID, function(elem){
  if (elem <= 20){return("A")}
  else if(elem <= 40){return("B")}
  else if(elem <= 60){return("C")}
  else if(elem <= 70){return("D")}
  else if(elem <= 100){return("E")}
})


df_new <- mutate( df_new, top_class = t_c)

Top tracks wise Energy Distribution
```{r}
t_energy <- ggplot(df_new, aes(x = energy, fill = top_class))+
  theme_bw() +
  geom_density( alpha= 0.3) +
  scale_fill_discrete(name="Category(Index Wise)", labels=c("A-Song(1-20)","B-Song(20-40)","C-Song(41-60)","D-Song(61-80)","E-Song(81-100)"))+
  labs( x ="Energy of tracks",
        title = "Distribution of Enerygy")
```


Top tracks wise acoustic-ness Distribution
```{r}
t_acoustic <- ggplot(df_new, aes(x = acousticness, fill = top_class))+
  theme_bw() +
  geom_density( alpha= 0.3) +
  scale_fill_discrete(name="Category(Index Wise)", labels=c("A-Song(1-20)","B-Song(20-40)","C-Song(41-60)","D-Song(61-80)","E-Song(81-100)"))+
  labs( x ="acousticness of tracks",
        title = "Distribution of Acousticness")
```


Top tracks wise loudness Distribution
```{r}
t_loudness <- ggplot(df_new, aes(x = loudness, fill = top_class))+
  theme_bw() +
  geom_density( alpha= 0.3) +
  scale_fill_discrete(name="Category(Index Wise)", labels=c("A-Song(1-20)","B-Song(20-40)","C-Song(41-60)","D-Song(61-80)","E-Song(81-100)"))+
  labs( x ="Loudness of tracks",
        title = "Distribution of Loudness")
```

Top tracks wise Popularity Distribution
```{r}
t_popularity <- ggplot(df_new, aes(x = track.popularity, fill = top_class))+
  theme_bw() +
  geom_density( alpha= 0.3) +
  scale_fill_discrete(name="Category(Index Wise)", labels=c("A-Song(1-20)","B-Song(20-40)","C-Song(41-60)","D-Song(61-80)","E-Song(81-100)"))+
  labs( x ="Popularity of tracks",
        title = "Distribution of Popularity")
```




figure <- ggarrange(t_energy, t_loudness, t_acoustic, t_popularity,
                    labels = c("A", "B", "C","D"),
                    ncol = 2, nrow = 2)





